---
title: "altOp Vignette"
author: "Kevin Tappe"
date: "2016-01-16"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{altOp Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


TODO: intro text to package `altOp`

We will use the dataset `CEOcomp` with data on CEO compensation in this vignette to illustrate the package's function. This dataset is part of the package. Here are the first 5 rows of `CEOComp` to give you an idea what the data looks like.
```{r, echo=FALSE, results='asis'}
library(altOp)
data(CEOcomp)
knitr::kable(head(CEOcomp, 5))
```


## altOp in combination with package 'broom'

  The package `broom`  is a package for ..TODO short explanation ...
  `altOp` is particularly useful in combination with some other packages such as broom.

  # allFormulas <- # TODO: list mit formulas generiert mit unseren Befehlen
  allFormulas <- list(form, form2, form3)

  # estimate all models specified by the various formulae
  allModels <- lapply(allFormulas, function(form) lm(form, data=CEOcomp))

  # save all tidied model results as list of data.frames
  library(broom)
  allModelResults <- lapply(allModels, function(mod) broom::tidy(mod))

  # TODO:
  #    * Place examples here how to rbind all the data.frames together in a useful format [variable estimates, t- and p-value in columns] (code is with KT) (maybe develop new way with dplyr?)
  #    * Also support row-wise format (like tidy format, but data is not "tidy" anymore)? Introduce column with model number and formula


## altOp in combination with stargazer and/or texreg
  library(stargazer)
  # TODO: fertigstellen: stargazer(allModels, type="text")

  library(texreg)
  ## TODO texreg(TODO)

  #TODO: Pixiedust?
  #TODO: sjPlot?



## Generate all formulae
### Example 1:
```{r}
# TODO: adapt parameters, function name etc., once the function is ready
ex1_depVar <- c("compvar") # dependend variable
ex1_opList <- list(c("roa", "roe", "tsr")) # various operationalizations of firm performance
ex1_fixVars <- c("emp", "marketcap") # fixed variables (to appear in all formulae)

ex1_all_formulae <- generiere_alle_formeln(abhVar = ex1_depVar,
                                           opList = ex1_opList,
                                           festVar = ex1_fixVars)

print(ex1_all_formulae)

```
This returns a list with 3 different formulae, because there are 3 different operationalisations for 1 varibale (firm performance).




### Example 2:

```{r}
# TODO: adapt parameters, function name etc., once the function is ready

ex2_depVar <- c("compvar") # dependend variable
ex2_opList <- list(c("roa", "roe", "tsr"), c("marketcap", "emp")) # various operationalizations for firm perf. and firm size
ex2_fixVars <- c("beta") # fixed variables (to appear in all formulae)

ex2_all_formulae <- generiere_alle_formeln(abhVar = ex2_depVar,
                                           opList = ex2_opList,
                                           festVar = ex2_fixVars)

print(ex2_all_formulae)
```
This returns a list with 6 different formulae, because there are 3 different operationalisations for firm performance and 2 different operationalizations for firm size (6 = 3 * 2).

TODO: note down general formula

